\section{Conclusion}
\label{sec:conc}
We addressed the problem of implicit feedback in spatial data and guidance by introducing \sgg , a novel and efficient interactive highlighting region approach for spatial data. We formulated our problem in form of a constrained optimization and proposed \sgg Algorithm, a greedy solution to highlight k-best points from IDRs - Interesting Dense Regions. We also propose the IDR Algorithm which consider mouse movements to create user preference regions to match user interesting points. We also introduce the discussion of genericness of our approach by materializing an example of apartment rental dataset. There are some directions of improvement for this work. Specifically, we want to consider an analyst profile vector which is built during interactive steps and will be exploited to return more analyst-tailored results.

We are also interested in analysing changes of user preferences over the time. Consider an user profile and her behaviour, we want to analyse the possibilities of change of region preference. Thus, we can verify if (and why) during a season the user prefers places in an area X of the city, while during the another season of the year the user would prefer an region Y, different of X. We can also analyse if there is changes by months or days, and also try to understand the reasons for these changes.

Some future extensions include the integration of generic query approach, and we also are going to consider an analyst profile vector which is built during interactive steps and will be exploited to return more analyst- tailored results.