\section{Related Work}\label{sec:related-works}

In this paper, we addressed the problem of highlighting geographical points to
guide analysts in consecutives steps. To the best of our knowledge, this is the
first work which formulates the geo-highlighting problem for recommending on
maps. However, our problem relates to a number of others as follows.     

Visual Highlighting. There has been efforts to highlight some pieces of
information in the huge heterogeneous data space so that the analyst can focus
on important aspects \cite{Liang2010,Lohmann:2012,Robinson2011}. Visual
Story Construction is another domain of work \cite{Segel:2010,Samet:2014} which
consecutive analysis steps are created automatically. However, all such highlighting methods are objective and does not consider analyst
interest. In GeoHiglight, we provide a simple yet effective feedback model which
can feed the recommendation algorithm to produce relevant results to current
investigations.        

Some other works have exploited highlighting as a technique to synchronize
coordinated views [CITE CROSSFILTER] or simplify complicated dataset
visualizations \cite{Robinson2011,Alper:2011}. Also in \cite{Philipsen}
different highlighting methods are compared in terms of efficiency and usefulness. Such methods are complementary to ours.     

Spatiotemporal Interactive Analysis and Visualization. Being an interactive
system, it should be efficient and capture user feedback and adapt the utility
function. In terms of efficiency, SpatialHadoop \cite{} and GeoSpark \cite{}
extend Hadoop and Spark ecosystems respectively to boost geographical
computations and visualizations. Such systems can be exploited as the backbone
of GeoHighlight once large-scale data needs to be analyzed.      

In terms of feedback, many off-the-shelf products such as Tableau \cite{} and
RapidMiner \cite{} are designed to visualize different kinds of datasets including
spatiotemporal ones. However, ``recommendation'' is the missing component in
most of such tools: providing a full package of operations and actions, the analyst
may know what to do next. In such system, analysis is usually considered as a
one-shot scenario, once in reality it happens in consecutive steps following
user feedback.        

Recommendation. There exist a huge body of work in recommendation
\cite{Adomavicius:2005} for various domains and datasets. However, spatial
dimension is still untouched and has not received a lot of attention. In
\cite{ChirigatiDDF16} a prediction algorithm for urban data is introduced which operates offline. In
\cite{Levandoski:2012,Magdy2014,HendawiKRBTA15a,Bao2015,Magdy:2014},
recommendation and visualization tools are introduced in specific domains.
However, most the such algorithms are not context-aware (based on user choices)
and does not consider diversity as a global metric.    
