\documentclass{sig-alternate-05-2015}
\usepackage{algorithm} 
\usepackage{algorithmic}
\usepackage{breqn}

 
\begin{document}

\setcopyright{acmcopyright}

%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\newtheorem{problem}{Problem}
\newtheorem{definition}{Definition}

 
% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

\conferenceinfo{EDBT}{2016}

\title{GeoHighlight: A Point-Recommendation Approach for Spatiotemporal Data}
%\subtitle{[Extended Abstract]

\numberofauthors{3}


\author{
Behrooz Omidvar-Tehrani$^{\dag}$, Gustavo Guerino$^{\ddag}$, Pl\'acido A. Souza Neto$^{\ddag}$\\
\affaddr{
$^{\dag}$The Ohio State University, USA, $^{\ddag}$Federal Institute of Rio Grande do Norte - IFRN, Brazil}\\
\affaddr{
$^{\dag}$\path{omidvar-tehrani.1@osu.edu},
$^{\ddag}$\path{gustavo.guerino@academico.ifrn.edu.br},
$^{\ddag}$\path{placido.neto@ifrn.edu.br}
}}

% \date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}

This paper proposes an approach towards generic visualization of
spatiotemporal data. Although the initial focus of our proposal is on urban
data, our framework was designed in a way to support any types of
\textit{geo} data such as flight data, bike data, smartphone GPS data, etc.
Highlighting spatiotemporal data is also a challenge that this work exploits, by using
recommendation algorithm to produce relevant results from datasets that has
geographic informations. We also discuss some directions and benefits of using
recommendation algorithm to highlight or retrieve important informations from
these kind of datasets.

\end{abstract}

\keywords{Interactive analysis; Spatiotemporal visualization; Urban data.}

\input{tex/intro}
\input{tex/datamodel}
\input{tex/problem}
\input{tex/algorithm}



\section{Scenarios}\label{sec:scenarios}

An analyst has different goals in mind once she needs analyzing data.
Considering the spatiotemporal dataset types aforementioned, we illustrate some
analyst's needs and challenges with the following two realistic scenarios.   
\bigskip

\textit{Scenario 1 - Taxi dataset:} Lucas is a taxi driver which works in New
York city. He wants to see if it is possible to improve his financial revenues
during the week. One option to Lucas may be to choose the potential better
points [$p_1, p_2, \ldots, p_n $] in a neighborhood [$n_1$] to stay considering
a week day and the time of work. He also wants to verify, once he dropoff an
client, which are the closest points [$cp_1, cp_2, \ldots, cp_n $] that can
offer him a new potential trip trajet back to [$n1$]. For instance, Lucas
finishes a trip trajet from a point $p_1$ in a neighborhood [$n_1$] to a point
$p_2$ in a neighborhood $n_2$.  So, given the point p2 in n2, which are the
potential closest points [$cp_1, cp_2, \ldots, cp_n $] (considering the
day/hours of the dropoff) that can bring him back to [$n_1$] with a new client
in a new trip with the small possible time of waiting.
\bigskip

\textit{Scenario 2 - Flight dataset}: Shadi is a flight analyst and she has to
propose new solutions for improve airport and flights performances. She wants to know:
(i) the best time of day/day of week/time of year to fly to minimise delays;
(ii) How does the number of people flying between different locations change
over time? And (iii) Is it possible to detect cascading failures as delays in
one airport create delays in others? And considering this fact, propose a
solution previously. In Shadi's working days she needs to propose quickly
solutions considering the mentioned aspects. 

% Table \ref{table:1} shows the operations for both scenarios.
% 
% \begin{table}[h!]
% \centering
% \begin{tabular}{||c c c ||} 
%  \hline
%  Col1 & Taxi scenario & Taxi scenario  \\ [0.5ex] 
%  \hline\hline
%  1 & 6 & 87837  \\ 
%  2 & 7 & 78  \\
%  3 & 545 & 778 \\
%  4 & 545 & 18744  \\
% 
%  \hline
% \end{tabular}
% \caption{Scenarios}
% \label{table:1}
% \end{table}



\section{Related Work}\label{sec:related-works}

In this paper, we addressed the problem of highlighting geographical points to
guide analysts in consecutives steps. To the best of our knowledge, this is the
first work which formulates the geo-highlighting problem for recommending on
maps. However, our problem relates to a number of others as follows.     

Visual Highlighting. There has been efforts to highlight some pieces of
information in the huge heterogeneous data space so that the analyst can focus
on important aspects \cite{Liang2010,Lohmann:2012,Robinson2011}. Visual
Story Construction is another domain of work \cite{Segel:2010,Samet:2014} which
consecutive analysis steps are created automatically. However, all such highlighting methods are objective and does not consider analyst
interest. In GeoHiglight, we provide a simple yet effective feedback model which
can feed the recommendation algorithm to produce relevant results to current
investigations.        

Some other works have exploited highlighting as a technique to synchronize
coordinated views [CITE CROSSFILTER] or simplify complicated dataset
visualizations \cite{Robinson2011,Alper:2011}. Also in \cite{Philipsen}
different highlighting methods are compared in terms of efficiency and usefulness. Such methods are complementary to ours.     

Spatiotemporal Interactive Analysis and Visualization. Being an interactive
system, it should be efficient and capture user feedback and adapt the utility
function. In terms of efficiency, SpatialHadoop \cite{} and GeoSpark \cite{}
extend Hadoop and Spark ecosystems respectively to boost geographical
computations and visualizations. Such systems can be exploited as the backbone
of GeoHighlight once large-scale data needs to be analyzed.      

In terms of feedback, many off-the-shelf products such as Tableau \cite{} and
RapidMiner \cite{} are designed to visualize different kinds of datasets including
spatiotemporal ones. However, ``recommendation'' is the missing component in
most of such tools: providing a full package of operations and actions, the analyst
may know what to do next. In such system, analysis is usually considered as a
one-shot scenario, once in reality it happens in consecutive steps following
user feedback.        

Recommendation. There exist a huge body of work in recommendation
\cite{Adomavicius:2005} for various domains and datasets. However, spatial
dimension is still untouched and has not received a lot of attention. In
\cite{ChirigatiDDF16} a prediction algorithm for urban data is introduced which operates offline. In
\cite{Levandoski:2012,Magdy2014,HendawiKRBTA15a,Bao2015,Magdy:2014},
recommendation and visualization tools are introduced in specific domains.
However, most the such algorithms are not context-aware (based on user choices)
and does not consider diversity as a global metric.    

\section{Conclusions}\label{sec:conclusions}


\bibliographystyle{abbrv}
\bibliography{main} 

\end{document}
