% THIS IS AN EXAMPLE DOCUMENT FOR VLDB 2012
% based on ACM SIGPROC-SP.TEX VERSION 2.7
% Modified by  Gerald Weber <gerald@cs.auckland.ac.nz>
% Removed the requirement to include *bbl file in here. (AhmetSacan, Sep2012)
% Fixed the equation on page 3 to prevent line overflow. (AhmetSacan, Sep2012)
 
\documentclass{vldb}
\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subfigure}
\usepackage{mathtools}
\usepackage{eurosym}

\usepackage{pgfplots}
\usepackage{url}
\usepackage{enumitem}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage[export]{adjustbox}
\usepackage{xspace}
\usepackage{breqn}

%\newcommand{\sgg}{{\sc PolyGuide}}
\newcommand{\sgg}{{\sc GeoPoly}}

% Include information below and uncomment for camera ready
%\vldbTitle{Towards Implicit Feedback Capturing on Spatial Data}
\vldbTitle{Polygon-based Feedback Capturing on Spatial Data}
\vldbAuthors{Behrooz Omidvar-Tehrani, Pl\'acido A. Souza Neto, Tiago Oliveira Lisboa, Francisco B. Silva Junior, Felipe F. Pontes}
\vldbDOI{https://doi.org/TBD}

\begin{document}

% ****************** TITLE ****************************************

%\title{Towards Implicit Feedback Capturing on Spatial Data}
\title{Polygon-based Feedback Capturing on Spatial Data}


% possible, but not really needed or used for PVLDB:
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available as\textit{Author's Guide to Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and BibTeX} at \texttt{www.acm.org/eaddress.htm}}}

% ****************** AUTHORS **************************************

% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Behrooz Omidvar-Tehrani\\
       \affaddr{University of Grenoble Alpes (France)}\\
       \email{behrooz.omidvar-tehrani@univ-grenoble-alpes.fr}
% 2nd. author
\alignauthor
Pl\'acido A. Souza Neto\\
       \affaddr{Federal Institute of Rio Grande do Norte (Brazil)}\\
       \email{placido.neto@ifrn.edu.br}
% 3rd. author
\alignauthor
Tiago Oliveira Lisboa\\
       \affaddr{Federal Institute of Rio Grande do Norte (Brazil)}\\
       \email{tiago.oliveira@\\academico.ifrn.edu.br}
\and
% 4th. author
\alignauthor
Francisco B. Silva Junior\\
       \affaddr{Federal Institute of Rio Grande do Norte (Brazil)}\\
       \email{bento.francisco@\\academico.ifrn.edu.br}
% 5th. author
\alignauthor
Felipe F. Pontes\\
       \affaddr{Federal Institute of Rio Grande do Norte (Brazil)}\\
       \email{freire.pontes@\\academico.ifrn.edu.br}
}

\maketitle


\begin{abstract}
Nowadays, spatial data are ubiquitous in various fields of science, such as transportation and social science. Discovering spatial patterns and trends provides improved insights into planning and decision making in various applications such as smart city management. A recent research direction in analyzing spatial data is to provide means for ``exploratory analysis'' of such data where analysts are guided towards interesting options in consecutive analysis iterations. Typically, the guidance component learns analyst's preferences using her explicit feedback, e.g., picking a spatial point or selecting a region of interest. However, it is often the case that analysts forget or don't feel necessary to explicitly express their feedback in what they find interesting. In this paper, we propose \sgg, an approach to capture implicit feedback on spatial data. The approach consists of observing mouse moves (as a means of analyst's interaction) in order to discover interesting spatial regions where the analyst has frequent mouse hovers. For an efficient discovery, we extend ST-DBSCAN and introduce a polygon-based abstraction layer for captured interactions. Using interesting regions, we highlight few points for the analyst to guide her in the analysis process. While we show the process of \sgg\ through a realistic example, we also briefly report on its efficiency and effectiveness.
\end{abstract}

\input{tex/intro}
\input{tex/datamodel}
\input{tex/problem}
\input{tex/algo}
\input{tex/exp}
\input{tex/rel}
\input{tex/conclusion}

\bibliographystyle{abbrv}
\bibliography{main}

\end{document}
